---
title: "Sum IXM data"
author: "Ruben Hermann"
date: '2022-06-20'
output: html_document
---

With this small script I want to sum up all the IXM counts per well. For the IXM count I added 50 µL fixed algae (1% PFA) with 150 µL of COOL 0 and let them sink in the well overnight. Then I took the Cy5 pictures with the IXM and with my custome module (ChlamyLugol10xRuben) counted them. Of each well 9 pictures were taken, therefore I will take the mean count for each well in this small script.

```{r setup}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Adding the summary function

```{r}

#################################################################################################################
#The generic sumarizing function I am using
## Summarizes data.
## Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   groupvars: a vector containing names of columns that contain grouping variables
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
  library(plyr)
  
  # New version of length which can handle NA's: if na.rm==T, don't count them
  length2 <- function (x, na.rm=FALSE) {
    if (na.rm) sum(!is.na(x))
    else       length(x)
  }
  
  # This does the summary. For each group's data frame, return a vector with
  # N, mean, and sd
  datac <- ddply(data, groupvars, .drop=.drop,
                 .fun = function(xx, col) {
                   c(N    = length2(xx[[col]], na.rm=na.rm),
                     mean = mean   (xx[[col]], na.rm=na.rm),
                     sd   = sd     (xx[[col]], na.rm=na.rm)
                   )
                 },
                 measurevar
  )
  
  # Rename the "mean" column    
  datac <- rename(datac, c("mean" = measurevar))
  
  datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
  
  # Confidence interval multiplier for standard error
  # Calculate t-statistic for confidence interval: 
  # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
  ciMult <- qt(conf.interval/2 + .5, datac$N-1)
  datac$ci <- datac$se * ciMult
  
  return(datac)
}



```



## Loading the files

```{r}
setwd('../../Data/IXM/raw_data')
#reading in the data
#Here I am loading each file from the directory in which is a .txt file
ALL <- NULL
temp= list.files(pattern=".txt")
for (i in 1:length(temp)){
  ALL[[i]]<-read.delim(temp[i], skip = 4, dec = '.')}

```

## Getting the mean of each well

```{r}
ALL_sum<-NULL
for (i in 1:length(ALL)) {
  ALL_sum[[i]] <- summarySE(ALL[[i]],measurevar="Cell.Count..ChlamyLugol10xRuben.",groupvars = c("MEASUREMENT.SET.ID","Well.Name"))
}

```

## Saving the sum of each well

```{r}
setwd('../../Data/IXM/raw_data_sum')
for ( i in 1:length(ALL_sum)) {
  name <- paste("Plate_ID",ALL_sum[[i]]$MEASUREMENT.SET.ID[1],".csv",sep="")
  write.csv(ALL_sum[[i]],file=name)
}

```


