---
  title: "Plotting time series"
author: "Ruben Hermann"
date: '2022-07-06'
output: html_document
---
  
  Now I want to apply the geber method on my data that I collected from my experiments of Chapter 3

```{r setup}
rm(list=ls())
library(tidyverse)
library(patchwork)
library(rstatix)
getwd()
```
## Seperating the different clone combinations

```{r}
all_dat <- read.csv("../../Data/Empirical Results/final_data.csv")
# Deleting the data, same as from statistics
all_dat <- subset(all_dat,id!=100)
all_dat$rt_ml[all_dat$rt_ml==0] <-NA


all_dat<-all_dat %>% convert_as_factor(fact_freq_def)
all_dat$levo_eco <- log(abs(all_dat$evo_eco))

all_dat<- do.call(data.frame,                      # Replace Inf in data by NA
                  lapply(all_dat,
                         function(x) replace(x, is.infinite(x), NA)))

all_dat$predprey <- all_dat$rt_ml/all_dat$algae_ml
all_dat$logpp <- log(all_dat$predprey)
all_dat$preypred <- all_dat$algae_ml/all_dat$rt_ml

###########################################################################################################
#Summing up the data for the different plotlinees

all_sum <- all_dat %>% 
  group_by(day,Clone.1,Clone.2,Freq.clone.1,fact_freq_def) %>%
  get_summary_stats(c(rt_ml,algae_ml,ln_cr,ln_rt,levo_eco,evo_eco,pred_freq_clone.1), type = "mean_se")

all_sum_m <- all_dat %>% 
  group_by(day,Clone.1,Clone.2) %>%
  get_summary_stats(c(rt_ml,algae_ml,ln_cr,ln_rt,levo_eco,evo_eco,pred_freq_clone.1), type = "mean_se")

########################################################################################################
#Separating the whole data 

CR1_6 <- data.frame()
CR2_6 <- data.frame()
CR1_7 <- data.frame()
CR2_7 <- data.frame()

for (i in 1:nrow(all_dat)){
  if(all_dat$Clone.1[i]=="CR1" & all_dat$Clone.2[i]=="CR6") CR1_6<-bind_rows(CR1_6,all_dat[i,])
  if(all_dat$Clone.1[i]=="CR1" & all_dat$Clone.2[i]=="CR7") CR1_7<-bind_rows(CR1_7,all_dat[i,])
  if(all_dat$Clone.1[i]=="CR2" & all_dat$Clone.2[i]=="CR6") CR2_6<-bind_rows(CR2_6,all_dat[i,])
  if(all_dat$Clone.1[i]=="CR2" & all_dat$Clone.2[i]=="CR7") CR2_7<-bind_rows(CR2_7,all_dat[i,])
}

#####################################################################################################
#Separating the mean grouped by: day,Clone.1,Clone.2,Freq.clone.1,fact_freq_def

CR1_6_mean <- data.frame()
CR2_6_mean <- data.frame()
CR1_7_mean <- data.frame()
CR2_7_mean <- data.frame()

for (i in 1:nrow(all_sum)){
  if(all_sum$Clone.1[i]=="CR1" & all_sum$Clone.2[i]=="CR6") CR1_6_mean<-bind_rows(CR1_6_mean,all_sum[i,])
  if(all_sum$Clone.1[i]=="CR1" & all_sum$Clone.2[i]=="CR7") CR1_7_mean<-bind_rows(CR1_7_mean,all_sum[i,])
  if(all_sum$Clone.1[i]=="CR2" & all_sum$Clone.2[i]=="CR6") CR2_6_mean<-bind_rows(CR2_6_mean,all_sum[i,])
  if(all_sum$Clone.1[i]=="CR2" & all_sum$Clone.2[i]=="CR7") CR2_7_mean<-bind_rows(CR2_7_mean,all_sum[i,])
}
#####################################################################################################
#Separating the mean grouped by: day,Clone.1,Clone.

CR1_6_mean_m <- data.frame()
CR2_6_mean_m <- data.frame()
CR1_7_mean_m <- data.frame()
CR2_7_mean_m <- data.frame()

for (i in 1:nrow(all_sum_m)){
  if(all_sum_m$Clone.1[i]=="CR1" & all_sum_m$Clone.2[i]=="CR6") CR1_6_mean_m<-bind_rows(CR1_6_mean_m,all_sum_m[i,])
  if(all_sum_m$Clone.1[i]=="CR1" & all_sum_m$Clone.2[i]=="CR7") CR1_7_mean_m<-bind_rows(CR1_7_mean_m,all_sum_m[i,])
  if(all_sum_m$Clone.1[i]=="CR2" & all_sum_m$Clone.2[i]=="CR6") CR2_6_mean_m<-bind_rows(CR2_6_mean_m,all_sum_m[i,])
  if(all_sum_m$Clone.1[i]=="CR2" & all_sum_m$Clone.2[i]=="CR7") CR2_7_mean_m<-bind_rows(CR2_7_mean_m,all_sum_m[i,])
}
```

## Plotting for CR1 with CR6

```{r}
p3<-ggplot(data=subset(CR1_6_mean,variable=="levo_eco"),aes(x=day,y=mean,color=fact_freq_def))+
  geom_line(size=3,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  theme_classic()+
  xlim(c(-0.3,8.3))+
  geom_point(size=4,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  geom_errorbar(aes(ymin=mean-se,ymax=mean+se),position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4),size=1,width=0.5)+
   geom_hline(aes(yintercept=0),size=1,color="black")+
  ggtitle("CR1 with CR6 ")+
  ylab("Log(|Evolution/Evcology|)")+xlab("Day")+
  ylim(c(-4,4))+
  labs(color = 'Starting freq of CR1')+
  theme(axis.ticks=element_line(size=4),
        axis.ticks.length=unit(.2, "cm"),
        axis.text = element_text(size=37),
        legend.position="none",
        legend.title =  element_blank(),
        axis.title=element_text(size=40),
        plot.title=element_blank())

p4<-ggplot(subset(CR1_6_mean,variable=="algae_ml"),aes(x=day,y=mean/100000,color=fact_freq_def))+
  geom_line(size=3,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  theme_classic()+
  ylim(c(0,25))+
  xlim(c(-0.3,8.3))+
  geom_point(size=4,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  ylab("Algae e+5 per ml")+xlab("Day")+
  ggtitle("CR1 with CR6 algal density")+
  geom_errorbar(aes(ymin=mean/100000-se/100000,ymax=mean/100000+se/100000),position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4),size=1,width=0.5)+
  theme(axis.ticks=element_line(size=4),
        axis.ticks.length=unit(.2, "cm"),
        axis.text = element_text(size=37),
        legend.position="none",
        axis.title=element_text(size=40),
        plot.title=element_blank(),
        axis.title.x=element_blank(),
        axis.text.x=element_blank())

p5<-ggplot(subset(CR1_6_mean,variable=="pred_freq_clone.1"),aes(x=day,y=mean,color=fact_freq_def))+
  geom_line(size=3,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  theme_classic()+
  ylim(c(0,1))+
  xlim(c(-0.3,8.3))+
  geom_point(size=4,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  ylab("Frequency of defended clone")+xlab("Day")+
  geom_errorbar(aes(ymin=mean-se,ymax=mean+se),position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4),size=1,width=0.5)+
  ggtitle("CR1 with CR6 frequency of defend clone")+
  theme(axis.ticks=element_line(size=4),
        axis.ticks.length=unit(.2, "cm"),
        axis.text = element_text(size=37),
        legend.position="none",
        axis.title=element_text(size=40),
        plot.title=element_blank(),
        axis.title.x=element_blank(),
        axis.text.x=element_blank())

p6<-ggplot(subset(CR1_6_mean,variable=="rt_ml"),aes(x=day,y=mean,color=fact_freq_def))+
  geom_line(size=3,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  theme_classic()+
  coord_cartesian(ylim=c(0,35)) + 
  scale_y_continuous(breaks=seq(0, 35, 5))+
  xlim(c(-0.3,8.3))+
  geom_point(size=4,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  ylab("Rotifer per ml")+xlab("Day")+
  ggtitle("CR1 with CR6")+
  geom_errorbar(aes(ymin=mean-se,ymax=mean+se),position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4),size=1,width=0.5)+
  theme(axis.ticks=element_line(size=4),
        axis.ticks.length=unit(.2, "cm"),
        axis.text = element_text(size=37),
        legend.position="none",
        axis.title=element_text(size=40),
        plot.title=element_text(size=50),
        axis.title.x=element_blank(),
        axis.text.x=element_blank())
```

## Plotting for CR1 with CR7

```{r}
p3_1<-ggplot(subset(CR1_7_mean,variable=="levo_eco"),aes(x=day,y=mean,color=fact_freq_def))+
  geom_line(size=3,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  theme_classic()+
  xlim(c(-0.3,8.3))+
  geom_point(size=4,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  geom_errorbar(aes(ymin=mean-se,ymax=mean+se),position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4),size=1,width=0.5)+
  geom_hline(aes(yintercept=0),size=1,color="black")+
  ggtitle("CR1 with CR7 ")+
  ylab("Log(|Evolution/Evcology|)")+xlab("Day")+
  ylim(c(-4,4))+
  labs(color = 'Starting freq of CR1')+
  theme(axis.ticks=element_line(size=4),
        axis.ticks.length=unit(.2, "cm"),
        legend.position="none",
        axis.title.x=element_text(size=40),
        axis.text.x=element_text(size=37),
        plot.title=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank())

p4_1<-ggplot(subset(CR1_7_mean,variable=="algae_ml"),aes(x=day,y=mean/100000,color=fact_freq_def))+
  geom_line(size=3,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  theme_classic()+
  ylim(c(0,25))+
  xlim(c(-0.3,8.3))+
  geom_point(size=4,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  ylab("Algae x 10^5 / mL")+xlab("Day")+
  ggtitle("CR1 with CR7 algal density")+
  geom_errorbar(aes(ymin=mean/100000-se/100000,ymax=mean/100000+se/100000),position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4),size=1,width=0.5)+
  theme(axis.ticks=element_line(size=4),
        axis.ticks.length=unit(.2, "cm"),
        legend.position="none",
        plot.title=element_blank(),
        axis.title=element_blank(),
        axis.text=element_blank())

p5_1<-ggplot(subset(CR1_7_mean,variable=="pred_freq_clone.1"),aes(x=day,y=mean,color=fact_freq_def))+
  geom_line(size=3,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  theme_classic()+
  ylim(c(0,1))+
  xlim(c(-0.3,8.3))+
  geom_point(size=4,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  ylab("Frequency of CR1")+xlab("Day")+
  geom_errorbar(aes(ymin=mean-se,ymax=mean+se),position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4),size=1,width=0.5)+
  ggtitle("CR1 with CR7 frequency of defend clone")+
  theme(axis.ticks=element_line(size=4),
        axis.ticks.length=unit(.2, "cm"),
        legend.position="none",
        plot.title=element_blank(),
        axis.title=element_blank(),
        axis.text=element_blank())

p6_1<-ggplot(subset(CR1_7_mean,variable=="rt_ml"),aes(x=day,y=mean,color=fact_freq_def))+
  geom_line(size=3,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  theme_classic()+
  coord_cartesian(ylim=c(0,35)) + 
  scale_y_continuous(breaks=seq(0, 35, 5))+
  xlim(c(-0.3,8.3))+
  geom_point(size=4,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  ylab("Rotifer / mL")+xlab("Day")+
  ggtitle("CR1 with CR7")+
  geom_errorbar(aes(ymin=mean-se,ymax=mean+se),position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4),size=1,width=0.5)+
  theme(axis.ticks=element_line(size=4),
        axis.ticks.length=unit(.2, "cm"),
        legend.position="none",
        plot.title=element_text(size=50),
        axis.title=element_blank(),
        axis.text=element_blank())
```
##########################################################################################################################
## Plotting for CR2 with CR6
#########################################################################################################################
```{r}
p3_2<-ggplot(subset(CR2_6_mean,variable=="levo_eco"),aes(x=day,y=mean,color=fact_freq_def))+
  geom_line(size=3,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  geom_point(size=4,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  geom_errorbar(aes(ymin=mean-se,ymax=mean+se),position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4),size=1,width=0.5)+
  theme_classic()+
  geom_hline(aes(yintercept=0),size=1,color="black")+
  ggtitle("CR2 with CR6")+
  ylab("Log(|Evolution/Evcology|)")+xlab("Day")+
  ylim(c(-4,4))+
  xlim(c(-0.3,8.3))+
  labs(color = 'Starting frequency \n of defended clone')+
  theme(axis.ticks=element_line(size=4),
        axis.ticks.length=unit(.2, "cm"),
        legend.position="none",
        legend.title = element_text(size=40),
        axis.title.x=element_text(size=40),
        axis.text.x=element_text(size=37),
        legend.text=element_text(size=40),
        plot.title=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank())

p4_2<-ggplot(subset(CR2_6_mean,variable=="algae_ml"),aes(x=day,y=mean/100000,color=fact_freq_def))+
  geom_line(size=3,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  theme_classic()+
  ylim(c(0,25))+
  xlim(c(-0.3,8.3))+
  geom_point(size=4,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  ylab("Algae x 10^5 / mL")+xlab("Day")+
  ggtitle("CR2 with CR6 algal density")+
  geom_errorbar(aes(ymin=mean/100000-se/100000,ymax=mean/100000+se/100000),position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4),size=1,width=0.5)+
  theme(axis.ticks=element_line(size=4),
        axis.ticks.length=unit(.2, "cm"),
        legend.position="none",
        plot.title=element_blank(),
        axis.title=element_blank(),
        axis.text=element_blank())

p5_2<-ggplot(subset(CR2_6_mean,variable=="pred_freq_clone.1"),aes(x=day,y=mean,color=fact_freq_def))+
  geom_line(size=3,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  theme_classic()+
  ylim(c(0,1))+
  geom_point(size=4,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  ylab("Frequency of CR2")+xlab("Day")+
  xlim(c(-0.3,8.3))+
  geom_errorbar(aes(ymin=mean-se,ymax=mean+se),position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4),size=1,width=0.5)+
  ggtitle("CR2 with CR6 frequency of defend clone")+
  theme(axis.ticks=element_line(size=4),
        axis.ticks.length=unit(.2, "cm"),
        legend.position="none",
        plot.title=element_blank(),
        axis.title=element_blank(),
        axis.text=element_blank())

p6_2<-ggplot(subset(CR2_6_mean,variable=="rt_ml"),aes(x=day,y=mean,color=fact_freq_def))+
  geom_line(size=3,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  theme_classic()+
  coord_cartesian(ylim=c(0,35)) + 
  scale_y_continuous(breaks=seq(0, 35, 5))+
  xlim(c(-0.3,8.3))+
  geom_point(size=4,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  ylab("Rotifer / mL")+xlab("Day")+
  ggtitle("CR2 with CR6")+
  geom_errorbar(aes(ymin=mean-se,ymax=mean+se),position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4),size=1,width=0.5)+
  theme(axis.ticks=element_line(size=4),
        axis.ticks.length=unit(.2, "cm"),
        legend.position="none",
        plot.title=element_text(size=50),
        axis.title=element_blank(),
        axis.text=element_blank())
```

## Plotting for CR2 with CR7

```{r}
p3_3<-ggplot(subset(CR2_7_mean,variable=="levo_eco"),aes(x=day,y=mean,color=fact_freq_def))+
  geom_line(size=3,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  geom_point(size=4,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  theme_classic()+
  xlim(c(-0.3,8.3))+
  geom_errorbar(aes(ymin=mean-se,ymax=mean+se),position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4),size=1,width=0.5)+
  geom_hline(aes(yintercept=0),size=1,color="black")+
  ggtitle("CR2 with CR7")+
  ylab("Log(|Evolution/Evcology|)")+xlab("Day")+
  ylim(c(-4,4))+
  labs(color = 'Starting frequency \n of defended clone')+
  theme(axis.ticks=element_line(size=4),
        axis.ticks.length=unit(.2, "cm"),
        axis.text = element_text(size=37),
        legend.position="right",
        legend.title = element_text(size=40),
        axis.title.x=element_text(size=40),
        axis.text.x=element_text(size=37),
         plot.title=element_blank(),
        legend.text=element_text(size=40),
        axis.title.y=element_blank(),
        axis.text.y=element_blank())

p4_3<-ggplot(subset(CR2_7_mean,variable=="algae_ml"),aes(x=day,y=mean/100000,color=fact_freq_def))+
  geom_line(size=3,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  theme_classic()+
  ylim(c(0,25))+
  xlim(c(-0.3,8.3))+
  geom_point(size=4,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  ylab("Algae x 10^5 / mL")+xlab("Day")+
  ggtitle("CR2 with CR7 algal density")+
  geom_errorbar(aes(ymin=mean/100000-se/100000,ymax=mean/100000+se/100000),position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4),size=1,width=0.5)+
    labs(color = 'Starting frequency \n of defended clone')+
  theme(axis.ticks=element_line(size=4),
        axis.ticks.length=unit(.2, "cm"),
        legend.position="right",
        legend.title = element_text(size=40),
        legend.text=element_text(size=40),
        plot.title=element_blank(),
        axis.title=element_blank(),
        axis.text=element_blank())

p5_3<-ggplot(subset(CR2_7_mean,variable=="pred_freq_clone.1"),aes(x=day,y=mean,color=fact_freq_def))+
  geom_line(size=3,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  theme_classic()+
  ylim(c(0,1))+
  xlim(c(-0.3,8.3))+
  geom_point(size=4,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  ylab("Frequency of CR2")+xlab("Day")+
  geom_errorbar(aes(ymin=mean-se,ymax=mean+se),position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4),size=1,width=0.5)+
  ggtitle("CR2 with CR7 frequency of defend clone")+
    labs(color = 'Starting frequency \n of defended clone')+
  theme(axis.ticks=element_line(size=4),
        axis.ticks.length=unit(.2, "cm"),
        legend.position="right",
        legend.title = element_text(size=40),
        legend.text=element_text(size=40),
        plot.title=element_blank(),
        axis.title=element_blank(),
        axis.text=element_blank())

p6_3<-ggplot(subset(CR2_7_mean,variable=="rt_ml"),aes(x=day,y=mean,color=fact_freq_def))+
  geom_line(size=3,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  theme_classic()+
  coord_cartesian(ylim=c(0,35)) + 
  scale_y_continuous(breaks=seq(0, 35, 5))+
  xlim(c(-0.3,8.3))+
  geom_point(size=4,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  ylab("Rotifer / mL")+xlab("Day")+
  ggtitle("CR2 with CR7")+
  geom_errorbar(aes(ymin=mean-se,ymax=mean+se),position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4),size=1,width=0.5)+
    labs(color = 'Starting frequency \n of defended clone')+
  theme(axis.ticks=element_line(size=4),
        axis.ticks.length=unit(.2, "cm"),
        legend.position="right",
        legend.title = element_text(size=40),
        legend.text=element_text(size=40),
        plot.title=element_text(size=50),
        axis.title=element_blank(),
        axis.text=element_blank())
```
#########################################################################################################################
## Creating a plot with all four different clonal lineage combinations

```{r}
figure_all <-p6+p6_1+p6_2+p6_3+
  p4+p4_1+p4_2+p4_3+
  p5+p5_1+p5_2+p5_3+ 
  p3+p3_1+p3_2+p3_3
guide_area()+plot_layout(ncol=4)
ggsave("../../Figures/Main/Figure 2.pdf",figure_all,width=50,height=50,limitsize = FALSE)
```

#########################################################################################################################
## Taking the data from the controls (only one clonal lineage present)

```{r}
all_dat <- read.csv("Empirical results/all_data_assembled.csv")
all_dat <- subset(all_dat,treat=="Control")

all_dat$fact_freq_def<- as.factor(all_dat$Freq.clone.1)
all_dat$ln_rt <- log(all_dat$rt_ml)
all_dat$ln_cr <- log(all_dat$algae_ml)

all_dat<- do.call(data.frame,                      # Replace Inf in data by NA
                  lapply(all_dat,
                         function(x) replace(x, is.infinite(x), NA)))
###########################################################################################################
#Summing up the data for the different plotlinees
all_sum <- all_dat %>% 
  group_by(day,Clone.1,Clone.2,Freq.clone.1,fact_freq_def) %>%
  get_summary_stats(c(rt_ml,algae_ml,ln_cr,ln_rt), type = "mean_se")


########################################################################################################
#Separating the whole data 
all_dat$clone<- "NULL"

for (i in 1:nrow(all_dat)){
  if(all_dat$Clone.1[i]=="CR1" & all_dat$Freq.clone.1[i]==1) all_dat$clone[i]="CR1"
  if(all_dat$Clone.1[i]=="CR2" & all_dat$Freq.clone.1[i]==1) all_dat$clone[i]="CR2"
  if(all_dat$Clone.2[i]=="CR6" & all_dat$Freq.clone.1[i]==0) all_dat$clone[i]="CR6"
  if(all_dat$Clone.2[i]=="CR7" & all_dat$Freq.clone.1[i]==0) all_dat$clone[i]="CR7"
}

#####################################################################################################
#Separating the mean grouped by: day,Clone.1,Clone.2,Freq.clone.1,fact_freq_def
all_sum$clone<- "NULL"

for (i in 1:nrow(all_sum)){
  if(all_sum$Clone.1[i]=="CR1" & all_sum$Freq.clone.1[i]==1) all_sum$clone[i]="CR1"
  if(all_sum$Clone.1[i]=="CR2" & all_sum$Freq.clone.1[i]==1) all_sum$clone[i]="CR2"
  if(all_sum$Clone.2[i]=="CR6" & all_sum$Freq.clone.1[i]==0) all_sum$clone[i]="CR6"
  if(all_sum$Clone.2[i]=="CR7" & all_sum$Freq.clone.1[i]==0) all_sum$clone[i]="CR7"
}
#####################################################################################################
```

## Plot controls

```{r}
p1_4<-ggplot(subset(all_sum,variable=="algae_ml"),aes(x=day,y=mean/100000,color=clone))+
  geom_line(size=3,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  theme_classic()+
  ylim(c(0,25))+
  xlim(c(-0.3,8.3))+
  geom_point(size=4,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  ylab("Algae e+5 per ml")+xlab("Day")+
  ggtitle("CR1 algal density")+
  geom_errorbar(aes(ymin=mean/100000-se/100000,ymax=mean/100000+se/100000),position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4),size=1,width=0.5)+
  scale_color_manual(values=c("#000066","#3366FF","#00FF33","#336600"))+
    labs(color = 'Clones in \n control')+
  theme(axis.ticks=element_line(size=4),
        axis.ticks.length=unit(.2, "cm"),
        legend.position="right",
        legend.title = element_text(size=40),
        legend.text=element_text(size=40),
        plot.title=element_text(size=50),
        axis.title=element_text(size=40),
        axis.text=element_text(size=37))

p2_4<-ggplot(subset(all_sum,variable=="rt_ml"),aes(x=day,y=mean,color=clone))+
  geom_line(size=3,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  theme_classic()+
  coord_cartesian(ylim=c(0,35)) + 
  scale_y_continuous(breaks=seq(0, 35, 5))+
  xlim(c(-0.3,8.3))+
  geom_point(size=4,position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4))+
  ylab("Rotifer per ml")+xlab("Day")+
  ggtitle("Controls")+
  geom_errorbar(aes(ymin=mean-se,ymax=mean+se),position = position_jitterdodge(jitter.height=0,jitter.width=0.1,dodge.width = 0.4),size=1,width=0.5)+
    scale_color_manual(values=c("#000066","#3366FF","#00FF33","#336600"))+
    labs(color = 'Clones in \n control')+
  theme(axis.ticks=element_line(size=4),
        axis.ticks.length=unit(.2, "cm"),
        legend.position="right",
        legend.title = element_text(size=40),
        legend.text=element_text(size=40),
        plot.title=element_text(size=50),
        axis.title.y=element_text(size=40),
        axis.text.y=element_text(size=37),
        axis.title.x=element_blank(),
        axis.text.x=element_blank())

figure_S4 <- p1_4 + p2_4 +guide_area()+plot_layout(ncol=4)
ggsave("../../Figures/Supplementary/Figure S1.pdf",figure_s4,width=30,height=50,limitsize = FALSE)
```
