---
title: "Analysis of time series"
author: "Ruben Hermann"
date: "2022-08-18"
output: html_document
---

```{r setup}
rm(list=ls())
library(tidyverse)
library(rstatix)
library(fitdistrplus)
library(nlme)
library(lme4)
data <- read.csv("../../Data/Empirical results/final_data.csv")
logit <- qlogis
```
## Transforming
separating the treatments, as I am not interested in the controls
cc: the clone combination in a single column
ln_cr: Natural log of algal density
ln_rt: Natural log of rotifer density
rt_data: including only data of interest for the statistcs:
Rep= replicate number (Random)
cc: Clone combination  (Treatment, fixed)
Freq.clone.1= starting frequency of the defended clone (Treatment, fixed)
ln_cr: density of algae (variable)
ln_rt: Density of rotifer (variable)
eco_evo: Log(abs(Ecological effect/Evolutionary effect)) calculated by geber method (variable)
rt_growth: Rotifer growth rate (variable)
logfreq: a logit transformation with the frequency data --> to create a "normal" distribution fo analysis

Im deleting Rep 10 (id100) from the CR1_CR7 + 0.7 (CR1) starting frequency as the rotifers failed to establish in this replicate
And Day 5 of id 181 (Rep 7) from CR1_CR6 + 0.6 (CR1) sarting frequency is also deleted, as no rotifers were acounted for
```{r}
data <- subset(data,treat=="Treatment")
data <- subset(data,id!=100)
data$rt_ml[data$rt_ml==0] <-NA

clone_comb=NULL
for (i in 1:nrow(data)) {
  clone_comb[i]=paste(data$Clone.1[i],"_",data$Clone.2[i],sep="")
}

data$cc <- clone_comb
data<-data %>% convert_as_factor(cc,Freq.clone.2,Rep)
data$ln_cr <- log(data$algae_ml)
data$ln_rt <- log(data$rt_ml)
data$leco_evo <- log(abs(data$eco_evo))
data$levo_eco <- log(abs(data$evo_eco))
data$day_fact<-as.factor(data$day)
data$logfreq <- logit(data$pred_freq_clone.2)

mean(data$levo_eco,na.rm=T)
```
## Analysis of algal density
### Step 1: Plotting for distribution

```{r}
cr_data <- data[complete.cases(data$algae_ml),]

ggplot(cr_data, aes(x=algae_ml)) + geom_histogram()
ggplot(cr_data, aes(x=algae_ml)) + geom_density()

min(cr_data$algae_ml)
max(cr_data$algae_ml)
#I will first check again for gamma and normal distribution
#For normal
m<-mean(cr_data$algae_ml)
v<-sqrt(var(cr_data$algae_ml))
gau<-data.frame(x=seq(1205,2840500,1000),y=length(cr_data$algae_ml)*200000*dnorm(seq(1205,2840500,1000),m,v))

#For gamma
rate <- mean(cr_data$algae_ml)/var(cr_data$algae_ml)
shape <- rate*mean(cr_data$algae_ml)
gam<-data.frame(x=seq(1205,2840500,1000),y=length(cr_data$algae_ml)*200000*dgamma(seq(1205,2840500,1000),shape,rate))


ggplot(cr_data, aes(x=algae_ml)) +
  geom_histogram()+
  geom_line(data=gau,aes(x=x,y=y),color="red")+
  geom_line(data=gam,aes(x=x,y=y),color="blue")

descdist(cr_data$algae_ml)
```
I went for a gamma distribution, because the normal distribution can also have negative values which is impossible to have with count_data

### Step 2: Statistical model
```{r}
contrasts(cr_data$cc) <- "contr.sum"
contrasts(cr_data$Freq.clone.2) <- "contr.sum"
cr_data$day_fact <- as.factor(cr_data$day)




m_cr <- glmer(algae_ml ~  cc*Freq.clone.2*day+(1|Rep) ,family =Gamma(link = "log"),data=cr_data)

summary(m_cr)
Anova(m_cr)
```

### Step 3: Validating the model
```{r}
cr_data$fit <- fitted(m_cr)

ggplot(cr_data,aes(x=algae_ml,y=fit))+
  geom_point()+
  geom_abline()

cr_data$res <- residuals(m_cr)

qplot(cr_data$res)
ggplot(cr_data, aes(sample=cr_data$res))+stat_qq()+stat_qq_line()
qplot(y=cr_data$res,x=seq(1,length(cr_data$res)),geom="point")+geom_hline(yintercept = 0)
qplot(x=cr_data$fit,y=cr_data$res)


plot(cr_data$res~cr_data$cc)
plot(cr_data$res~cr_data$Freq.clone.2)
plot(cr_data$res~cr_data$day_fac)
```
This looks good enough for now!
 
## Analysis of rotifer density
 
### Step 1: Plotting for distribution
```{r}
rt_data <- data[complete.cases(data$rt_ml),]

ggplot(rt_data, aes(x=ln_rt)) + geom_histogram(binwidth=.5)
ggplot(rt_data, aes(x=ln_rt)) + geom_density()


min(rt_data$ln_rt)
max(rt_data$ln_rt)
#I will first check again for gamma and normal distribution
#For normal
m<-mean(rt_data$ln_rt)
v<-sqrt(var(rt_data$ln_rt))
gau<-data.frame(x=seq(-2,5,0.01),y=length(rt_data$ln_rt)*0.1*dnorm(seq(-2,5,0.01),m,v))

#For gamma
rate <- mean(rt_data$ln_rt)/var(rt_data$ln_rt)
shape <- rate*mean(rt_data$ln_rt)
gam<-data.frame(x=seq(-2,5,0.01),y=length(rt_data$ln_rt)*0.1*dgamma(seq(-2,5,0.01),shape,rate))


ggplot(rt_data, aes(x=ln_rt)) + geom_histogram(binwidth=0.1)+
  geom_line(data=gau,aes(x=x,y=y),color="red")+
  geom_line(data=gam,aes(x=x,y=y),color="blue")

descdist(rt_data$rt_ml)
descdist(rt_data$ln_rt)
```
Even though it could be a better fit, I will use the gaussian distribution --> gamma canno be negative
Will needed to be revisted!!

### Step 2: Statistical model

```{r}
contrasts(rt_data$cc) <- "contr.sum"
contrasts(rt_data$Freq.clone.2) <- "contr.sum"

m_rt <- lmer(ln_rt ~  cc*Freq.clone.2+day+(1|Rep) ,data=rt_data)
summary(m_rt)
Anova(m_rt)
```

### Step 3: Validating the model

```{r}
rt_data$fit <- fitted(m_rt)


ggplot(rt_data,aes(x=ln_rt,y=fit))+
  geom_point()+
  geom_abline()

rt_data$res <- residuals(m_rt2)

qplot(rt_data$res)
ggplot(rt_data, aes(sample=rt_data$res))+stat_qq()+stat_qq_line()
qplot(y=rt_data$res,x=seq(1,length(rt_data$res)),geom="point")+geom_hline(yintercept = 0)
qplot(x=rt_data$fit,y=rt_data$res)


plot(rt_data$res~rt_data$cc)
plot(rt_data$res~rt_data$Freq.clone.1)
plot(rt_data$res~rt_data$day_fac)


```
The model has some issues with the low values/outliars + real vs fitted values is the slope a bit wrong --> for now I will keep it but for the real manuscript I will need to revise it --> good enough for now due to time limit


## Analysis of frequency data
### Step 1: Plotting for distribution
```{r}
freq_data <- data[complete.cases(data$pred_freq_clone.2),]

ggplot(freq_data, aes(x=logfreq)) + geom_histogram(binwidth=.1)
ggplot(freq_data, aes(x=logfreq)) + geom_density()

freq_data <-freq_data[!is.infinite(freq_data$logfreq),]
descdist(freq_data$logfreq)

min(freq_data$logfreq)
max(freq_data$logfreq)
#I will first check again for gamma and normal distribution
#For normal
m<-mean(freq_data$logfreq)
v<-sqrt(var(freq_data$logfreq))
gau<-data.frame(x=seq(-4,4,0.01),y=length(freq_data$logfreq)*0.1*dnorm(seq(-4,4,0.01),m,v),name="Gaussian")
logn <-data.frame(x=seq(-4,4,0.01),y=length(freq_data$logfreq)*0.1*dlnorm(seq(-4,4,0.01)),name="Lognorml")

#For gamma
rate <- mean(freq_data$logfreq)/var(freq_data$logfreq)
shape <- rate*mean(freq_data$logfreq)
gam<-data.frame(x=seq(-4,4,0.01),y=length(freq_data$logfreq)*0.1*dgamma(seq(-4,4,0.01),shape,rate),name="Gamma")

ggplot(freq_data, aes(x=logfreq)) + geom_histogram(binwidth=0.1)+
  geom_line(data=gau,aes(x=x,y=y,color=name),color="red")
```
Gaussian, so normal, distribution seems really good here!

### Step 2: Statistical model
```{r}
contrasts(freq_data$cc) <- "contr.sum"
contrasts(freq_data$Freq.clone.2) <- "contr.sum"

m_freq<-lmer(logfreq~cc*Freq.clone.2*day_fact+(1|Rep),data=freq_data)
summary(m_freq)
Anova(m_freq)
```

### Step 3: Validating the model

```{r}
freq_data$fit <- fitted(m_freq)

ggplot(freq_data,aes(x=logfreq,y=fit))+
  geom_point()+
  geom_abline()

freq_data$res <- residuals(m_freq)

qplot(freq_data$res)
ggplot(freq_data, aes(sample=freq_data$res))+stat_qq()+stat_qq_line()
qplot(y=freq_data$res,x=seq(1,length(freq_data$res)),geom="point")+geom_hline(yintercept = 0)
qplot(x=freq_data$fit,y=freq_data$res)


plot(freq_data$res~freq_data$cc)
plot(freq_data$res~freq_data$Freq.clone.1)
plot(freq_data$res~freq_data$day_fac)
```
The predictions are still rather of from the real data, a tendency can be seen. But the model still needs to be imrpoved --> as well still keeping it for now due to time reasons
Needs to eb revisted later!


## Analysis of log(abs(evo over eco))  -->
### Step 1: Plotting for distribution
```{r}
levo_eco_data<- do.call(data.frame,                      # Replace Inf in data by NA
                  lapply(data,
                         function(x) replace(x, is.infinite(x), NA)))

levo_eco_data <- levo_eco_data[complete.cases(levo_eco_data$levo_eco),]

ggplot(levo_eco_data, aes(x=logfreq)) + geom_histogram(binwidth=.1)
ggplot(levo_eco_data, aes(x=logfreq)) + geom_density()

descdist(levo_eco_data$levo_eco)

min(levo_eco_data$levo_eco)
max(levo_eco_data$levo_eco)
#I will first check again for gamma and normal distribution
#For normal
m<-mean(levo_eco_data$levo_eco)
v<-sqrt(var(levo_eco_data$levo_eco))
gau<-data.frame(x=seq(-9,7,0.01),y=length(levo_eco_data$levo_eco)*0.1*dnorm(seq(-9,7,0.01),m,v),name="Gaussian")
logn <-data.frame(x=seq(-9,7,0.01),y=length(levo_eco_data$levo_eco)*0.1*dlnorm(seq(-9,7,0.01)),name="Lognorml")

#For gamma
rate <- mean(levo_eco_data$levo_eco)/var(levo_eco_data$levo_eco)
shape <- rate*mean(levo_eco_data$levo_eco)
gam<-data.frame(x=seq(-9,7,0.01),y=length(levo_eco_data$levo_eco)*0.1*dgamma(seq(-9,7,0.01),shape,rate),name="Gamma")

ggplot(levo_eco_data, aes(x=levo_eco)) + geom_histogram(binwidth=0.1)+
  geom_line(data=gau,aes(x=x,y=y,color=name),color="red")

```
Gaussian, so normal, distribution seems really good here!

### Step 2: Statistical model
```{r}
contrasts(levo_eco_data$cc) <- "contr.sum"

m_levo<-lmer(levo_eco~cc*day_fact+Freq.clone.2+(1|Rep),data=levo_eco_data,contrasts =contr.sum)



summary(m_levo)
Anova(m_levo)

TukeyHSD(m_levo)
```

### Step 3: Validating the model

```{r}
levo_eco_data$fit <- fitted(m_levo)

ggplot(levo_eco_data,aes(x=levo_eco,y=fit))+
  geom_point()+
  geom_abline()

levo_eco_data$res <- residuals(m_levo)

qplot(levo_eco_data$res)
ggplot(levo_eco_data, aes(sample=levo_eco_data$res))+stat_qq()+stat_qq_line()
qplot(y=levo_eco_data$res,x=seq(1,length(levo_eco_data$res)),geom="point")+geom_hline(yintercept = 0)
qplot(x=levo_eco_data$fit,y=levo_eco_data$res)


plot(levo_eco_data$res~levo_eco_data$cc)
```

### Rotifer density at day 8
This is not from the time series, but another good analysis for the results
--> as I can say that the final density is the same over all group but we have a "hidden" eco-evo dynamics for them depending on the clonal combination

```{r}
d8 <- subset(data,day==8)

shapiro.test(d8$rt_ml)
#W = 0.94237, p-value = 8.882e-05

d8 %>% levene_test(rt_ml~cc)
#p=0.616191

kruskal.test(d8$rt_ml~d8$cc)
#Kruskal-Wallis chi-squared = 0.95525, df = 3, p-value = 0.8121
```

Final density do not differ between the clonal combination, but the way there is significantly different